Spin canonical rings of log stacky curves

### 2015-07-10 curves-write-up/spin-cring.tex
delete remaining comments

\begin{rem}
\label{rem:explicit-generators}
%The main theorem obtains bounds on the degrees of the generators
%and relations of log spin canonical rings. 
In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
of the genus one and genus zero cases of our main theorem also yield explicit systems
of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
Furthermore, our proof of the genus $g \geq 2$ case provides
an inductive procedure for explicitly determining the generators
and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.  Many
explicit systems of generators and relations for curves of genus $2
\leq g \leq 15$ are detailed in interesting examples by Neves
\cite[Section III.4]{neves:halfcan}. 
\end{rem}

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. 
%Note that the elements $t_1, \ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$. Hence, by a dimension count, these sections form a $k$-basis for
%$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}
%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
\]
so the mediant inequality tells us
\[
	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
\]
Multiplying through by $k_i$ gives
\[
	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

@@

Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so 
%  The argument goes $c_i d \ge c k_i$
% implies c_i \frac{k}{k_i} \ge c
% implies c_i + \frac{k-k_i}{k_i}c_i \ge c
% \implies c_i (k-k_i) \frac{c_i}{k_i}\ge c
% so since everything is an integer $c_i +\lfloor (k - k_i) \frac{c_i}{k_i}\rfloor \ge c$
% \implies the equation below:
\[
	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
\]
which implies
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
\end{equation}

>>>>

\begin{rem}
\label{rem:explicit-generators}
In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
of the genus one and genus zero cases of our main theorem also yield explicit systems
of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
Furthermore, our proof of the genus $g \geq 2$ case provides
an inductive procedure for explicitly determining the generators
and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.  Many
explicit systems of generators and relations for curves of genus $2
\leq g \leq 15$ are detailed in interesting examples by Neves
\cite[Section III.4]{neves:halfcan}. 
\end{rem}

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. 
Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
\]
so the mediant inequality tells us
\[
	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
\]
Multiplying through by $k_i$ gives
\[
	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

@@

Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
\[
	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
\]

\noindent
which implies
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
\end{equation}
